MCTS Based on Simple Regret

### 2012-02-22 slides/slides.tex
voi-aware sampling
all goes well

@@

>>>>

\begin{frame}{VOI-aware sampling}

\begin{itemize}
\item Chooses an action with the maximum VOI estimate.
\item Estimates the VOI based on bounds on:
  \begin{itemize}
  \item the probability that one or more rollouts will make another
    action appear better than the current best;
  \item the gain that may be incurred if such a change occurs.
  \end{itemize}
\end{itemize}
\begin{eqnarray*}
VOI_\alpha&\approx&\frac {\overline X_\beta} {n_\alpha+1}
\exp\left(-2(\overline X_\alpha - \overline X_\beta)^2 n_\alpha\right)\\
VOI_i&\approx&\frac {1-\overline X_\alpha} {n_i+1}
\exp\left(-2(\overline X_\alpha - \overline X_i)^2 n_i\right),\; i\ne\alpha\nonumber\\
\mbox{where }&&\alpha=\arg\max_i \overline X_i,\quad
             \beta=\arg\max_{i,\,i\ne\alpha} \overline X_i\nonumber
\end{eqnarray*}
\end{frame}

@@

\begin{frame}{Summary}
\begin{itemize}
\item<+-> Improved MCTS scheme, SRCR, introduced.
\item<+-> SRCR performs better than unmodified UCT.
\item<+-> VOI-aware sampling for minimizing sampling regret proposed.
\item<+-> Better sampling schemes can be developed based on principles
  of Rational Metareasoning.
\item<+-> UCT is not well understood. Better understanding will help
  in developing efficient  MCTS schemes and adapting to different domains.
\end{itemize}
\end{frame}

\begin{frame}{}
\begin{center}
\LARGE{Thank you!}
\end{center}
\end{frame}
